MSDS6372Project1

### 2021-02-02 MSDS6372Project1.Rmd
tried scaling method, commented out

#getting training response
trainY = train$MSRP
#getting training predictors
trainX = train[,-c(1,2,4,7,8,10,11,15,16,17,18,19,20,21,22,23,24,25,26)]
# Doing the same for test
testY = test$MSRP
testX = test[,-c(1,2,4,7,8,10,11,15,16,17,18,19,20,21,22,23,24,25,26)]

>>>>

#getting training response
trainY = train$MSRP
#getting training predictors
trainX = train[,-c(1,2,4,7,8,10,11,15,16,17,18,19,20,21,22,23,24,25,26)]
#try scaling variables
#str(trainX)
#for(i in 1: dim(trainX)[2]){
#  trainX[,i] = scale(trainX[,i])
#}
# finished scaling
# Doing the same for test
testY = test$MSRP
testX = test[,-c(1,2,4,7,8,10,11,15,16,17,18,19,20,21,22,23,24,25,26)]
#str(testX)
#for(i in 1: dim(testX)[2]){
#  testX[,i] = scale(testX[,i])
#}
